---
title:  | 
  | Item Drift
  | Report
date: '`r paste("Report Date: ", Sys.Date())`'
always_allow_html: yes
pagetitle: "Item Drift Report"
output: 
    pdf_document:
      df_print: default
      toc: yes
    html_document:
      toc: true
      toc_depth: 3
      toc_float: true
      self_contained: yes
      mode: selfcontained
      theme: journal
    word_document:
      df_print: default
      toc: yes
      toc_depth: '4'
header-includes:
  - \usepackage{fancyhdr}
  - \pagestyle{fancy}
  - \fancyhead[C]{Item Drift Analysis}
  - \fancyfoot[C]{REPORT}
  - \fancyfoot[L]{\thepage}
  - \usepackage{comment}
  - \usepackage{float}
  - \usepackage{booktabs}
  - \usepackage{makecell}
params:
  report_format: NA,
  all_item_plot: NA,
  separate_item_plot: NA, 
  item_time_analysis: NA
---
```{r setup, include=F}
# Libraries
library(kableExtra)
library(flextable)

# Global options
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
flextable::set_flextable_defaults(fonts_ignore=TRUE) # or get warnings

# Printing options depending on report format
if(params$report_format == 'html'){
  options(knitr.table.format = 'html')
  } else if (params$report_format == 'pdf') {
    options(knitr.table.format = 'latex')
  } else {
    options(knitr.table.format = 'markdown')
  }
```

`r if(params$report_format != "docx") {"\\begin{comment}"}`

# Item Drift Report

`r if(params$report_format != "docx") {"\\end{comment}"}`

## Item Analysis

Logistic regression mixed-effects models were constructed with items and time, grouped into selected intervals, as main effects, with an interaction term, and person nested within any optional grouping variables as random effects. Linear and quadratic models were considered. The best fitting model was compared with a reduced model and any items with significant interaction effects with time were identified. The interpretation is that any items identified below varied in difficulty over time.

```{r item-analysis}
params$item_time_analysis %>% 
  table_print(., caption = "Significant Items")
```

## All Items Plot of Difficulty Over Time
```{r all-items-plot, results = 'asis'}
params$all_item_plot
```

## Individual Items Plot of Difficulty Over Time

```{r separate-items-plot, results = 'asis'}
params$separate_item_plot
```

<!-- insert logo -->
```{r, echo=FALSE, message=F, warning=F, fig.align="center", out.width= '50%', out.height= '50%'}
# Add logo to output
library(jpeg)
library(grid)
library(gridExtra)
# url <- "https://provexam.com/wp-content/uploads/2020/10/Prov_Logo_Cropped.png"
# z <- tempfile()
# download.file(url,z,mode="wb")
# img <- readJPEG(z)
# rimg <- rasterGrob(as.raster(img)) # raster multilayer object
tg <- textGrob("Prov Exam", gp=gpar(fontfamily = "serif", fontsize = 20))
sg1 <- textGrob("www.provexam.com", gp=gpar(fontfamily = "sans", fontsize = 10))
sg2 <- textGrob("150 W Civic Ctr Dr Suite 601", gp=gpar(fontfamily = "sans", fontsize = 10))
sg3 <- textGrob("Sandy, UT 84070", gp=gpar(fontfamily = "sans", fontsize = 10))
sg4 <- textGrob("support@provexam.com", gp=gpar(fontfamily = "sans", fontsize = 10))
sg5 <- textGrob("(801)-733-4455", gp=gpar(fontfamily = "sans", fontsize = 10))
lay <- rbind(
             c(1,NA),
             c(1,NA),
             c(1,NA),
             c(1,2),
             c(1,3),
             c(1,4),
             c(1,5),
             c(1,6),
             c(1,7),
             c(1,NA),
             c(1,NA),
             c(1,NA),
             c(1,NA))
# grid.arrange(rimg, tg, sg1, sg2, sg3, sg4, sg5, layout_matrix = lay)
grid.arrange(tg, sg1, sg2, sg3, sg4, sg5, layout_matrix = lay)
grid.rect(width = 1.5, height = .5, gp = gpar(lwd = 2, col = "blue", fill = NA))
```
&nbsp;

<!-- html contact links footer -->
```{r contact_info, echo=FALSE, results= 'asis'}
  cat("<p style=\"text-align:
      center;\"><a href=\"https://www.provexam.com\" target = \"_blank\">Prov Exam</a></p>")
if (params$report_format == "html"){
  cat("<p style=\"text-align: center;\"><a style=\"color: #0645AD;\" href = \"mailto:support@provexam.com?subject = Item Drift&body = Message\"><em>Email Prov for support</em></a></p>")
}
```

```{r, include=FALSE}
options(tinytex.verbose = TRUE)
```

